---
title: "Interpretative"
author: "Hai Liang"
date: "10/17/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load library

```{r}
library(RSiena)
```

Load datasets

```{r}
load("user.Rdata")
load("activity.Rdata")
load("attribute.Rdata") #ideology and other attributes
load("disnet_all4.Rdata")
load("bipnet_all4.Rdata")
```

Estimate effects between two consective periods. Set t=1 to estimate effects between period 1 and period 2.

```{r}
t=1 #time period
```

There are 341 participants in periods 1&2.

```{r}
participants<-c(user[[t]],user[[t+1]])[duplicated(c(user[[t]],user[[t+1]]))]
```

Prepare attribute data for the participants

```{r}
attr<-attribute[which(attribute$participant%in%participants),c("participant","leanR")]
attr<-attr[order(attr[,1]),]
attr$ideology[attr$leanR=="right"]=1
attr$ideology[attr$leanR=="central"]=2
attr$ideology[attr$leanR=="left"]=3
```

Read the discussion networks in periods 1&2:

```{r}
dis1 <- as.matrix(disnet[[t]])[rownames(disnet[[t]]) %in% participants,colnames(disnet[[t]]) %in% participants]
dis2 <- as.matrix(disnet[[t+1]])[rownames(disnet[[t+1]]) %in% participants,colnames(disnet[[t+1]]) %in% participants]
```

Dichotomize the networks into unweighted networks:

```{r}
min=9
max=10000

dis1[dis1<min | dis1>=max]=0
dis2[dis2<min | dis2>=max]=0

dis1[dis1>=min]=1
dis2[dis2>=min]=1
```

Read the interpretative framework networks in period2 1&2:

```{r}
bipnet1<-as.matrix(bipnet[[t]])[rownames(bipnet[[t]]) %in% participants,]
bipnet2<-as.matrix(bipnet[[t+1]])[rownames(bipnet[[t+1]]) %in% participants,]
```

Select the top 50 edges (word-coocurrence):

```{r}
y=as.data.frame(colSums(bipnet1)+colSums(bipnet2))
y[,2]=rownames(y)
y=y[order(y[,1],decreasing=T),]
namelist<-rownames(y)[1:50]

bipnet1<-bipnet1[,colnames(bipnet1)%in% namelist]
bipnet2<-bipnet2[,colnames(bipnet2)%in% namelist]
```

Dichotomize the networks into unweighted networks:

```{r}
cut=1
bipnet1[bipnet1<cut]=0
bipnet2[bipnet2<cut]=0

bipnet1[bipnet1>=cut]=1
bipnet2[bipnet2>=cut]=1
```

Set bipartite network object:

```{r}
# find out number of nodes in nodesets:
nrUsers <- dim(bipnet1)[1]
nrEdges <- dim(bipnet1)[2]

# define different node sets:
Users <- sienaNodeSet(nrUsers, nodeSetName="Users")
Edges <- sienaNodeSet(nrEdges, nodeSetName="Edges")
```

Prepare objects for SIENA estimations:

```{r}
# identify dependent variables for the analysis;
# start with bipartite network:
wordassc <- sienaNet(array(c(bipnet1,bipnet2),dim=c(nrUsers,nrEdges,2)),"bipartite",nodeSet=c("Users","Edges"))

# now add the normal network:
dis <- sienaNet(array(c(dis1, dis2),dim=c(nrUsers,nrUsers,2)),nodeSet="Users")

# covariates
ideology <- coCovar(attr$ideology,nodeSet="Users")
activity <- coCovar(sqrt(activity[activity$sender%in%participants,t+2]), nodeSet="Users")

# combine data for the analysis:
bipData <- sienaDataCreate(dis,wordassc,ideology,activity,nodeSets=list(Users,Edges))
```

Model specification: choose statistics (mechanisms) to estimate

```{r}
# get effects table for model specification:
bipEffects <- getEffects(bipData)

# generate initial descriptive outputfile:
# print01Report(bipData,bipEffects,modelname="Bipartite-illustration")

# Take a look at the generated output file "Bipartite-illustration.out"
# to see how RSiena interpreted the directives provided.

# Specify the model:
bipEffects <- includeEffects(bipEffects,transTrip,inPop,name="dis")
bipEffects <- includeEffects(bipEffects,sameX,interaction1="ideology")
bipEffects <- includeEffects(bipEffects,from,name="dis",interaction1="wordassc")
bipEffects <- includeEffects(bipEffects,egoX,altX,name="dis",interaction1="activity")

bipEffects <- includeEffects(bipEffects,inPop,outInAss,name="wordassc")
bipEffects <- includeEffects(bipEffects,to,outActIntn,name="wordassc",interaction1="dis")
bipEffects <- includeEffects(bipEffects,sameWXClosure,name="wordassc",interaction1="dis",interaction2 = "ideology")
bipEffects <- includeEffects(bipEffects,toSameX,name="wordassc",interaction1="dis",interaction2="ideology")


# Create model object:
bipModel <- sienaModelCreate(useStdInits=FALSE,projname='bipartite-Glasgow-results',cond=F)
bipModel
```

Estimation

```{r}
# Estimate model:
bipResults <- siena07(bipModel,data=bipData,effects=bipEffects,useCluster=T, initC=T,
                      nbrNodes=6,batch=T,verbose=F,returnDeps=TRUE)

bipModel <- sienaModelCreate(useStdInits=FALSE,projname='bipartite-Glasgow-results',cond=F,nsub=4,n3=6000,firstg=0.1)

bipResults <- siena07(bipModel,data=bipData,effects=bipEffects,
                      prevAns = bipResults,
                      useCluster=T, initC=T,nbrNodes=6,batch=T,verbose=F,returnDeps=TRUE)
bipResults
```
