---
title: "Semantic"
author: "Hai Liang"
date: "10/15/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load library

```{r}
library(RSiena)
```

Load dataset

```{r}
load("user.Rdata") # participants in the 4 periods
load("activity.Rdata") # number of posts in the 4 periods for each user
load("attribute.Rdata") #ideology and other attributes
load("disnet_all4.Rdata") # discussion network matrix in the 4 periods
load("semantic_all4_directless.Rdata") # semantic similarity matrix in the 4 periods
```

Estimate effects between two consective periods. Set t=1 to estimate effects between period 1 and period 2.

```{r}
t=1 #time period
```

There are 341 participants in periods 1&2.

```{r}
participants<-c(user[[t]],user[[t+1]])[duplicated(c(user[[t]],user[[t+1]]))]
```

Prepare attribute data for the participants

```{r}
attr<-attribute[which(attribute$participant%in%participants),c("participant","leanR")]
attr<-attr[order(attr[,1]),] # sort by participants name
attr$ideology[attr$leanR=="right"]=1
attr$ideology[attr$leanR=="central"]=2
attr$ideology[attr$leanR=="left"]=3
```

Read the discussion networks in periods 1&2:

```{r}
dis1 <- as.matrix(disnet[[t]])[rownames(disnet[[t]]) %in% participants,colnames(disnet[[t]]) %in% participants]
dis2 <- as.matrix(disnet[[t+1]])[rownames(disnet[[t+1]]) %in% participants,colnames(disnet[[t+1]]) %in% participants]
```

Dichotomize the networks into unweighted networks:

```{r}
min=9
max=10000

dis1[dis1<min | dis1>=max]=0
dis2[dis2<min | dis2>=max]=0

dis1[dis1>=min]=1
dis2[dis2>=min]=1
```

Read the semantic similarity networks in period2 1&2:

```{r}
ss1 <- as.matrix(semantic[[t]])[rownames(semantic[[t]]) %in% participants,colnames(semantic[[t]]) %in% participants]
ss2 <- as.matrix(semantic[[t+1]])[rownames(semantic[[t+1]]) %in% participants,colnames(semantic[[t+1]]) %in% participants]
```

Dichotomize the networks into unweighted networks:

```{r}
cut=0.34

ss1[ss1<cut]=0
ss2[ss2<cut]=0

ss1[ss1>=cut]=1
ss2[ss2>=cut]=1
```

Prepare objects for SIENA estimations:

```{r}
# Identify dependent variables for the analysis;
ss <- sienaNet(array(c(ss1,ss2), dim=c(nrow(dis1),ncol(dis1),2)))
dis <- sienaNet(array(c(dis1,dis2), dim=c(nrow(dis1),ncol(dis1),2)))

# Identify constant covariate:
ideology <- coCovar(attr$ideology)
activity <- coCovar(sqrt(activity[which(activity$sender%in%participants),t+2]))

# Combine data for the analysis:
MutiplexData <- sienaDataCreate(dis,ss,ideology,activity)
```

Model specification: choose statistics (mechanisms) to estimate

```{r}
# Get effects table for model specification:
MutiplexEffects <- getEffects(MutiplexData) # by defaut the model includes rate, degree, reciprocity effects

# transitivity and 3-cycle effects for the evolution of SS and DIS:
MutiplexEffects <- includeEffects(MutiplexEffects,transTriads,inPop,name="ss") # add 3-cycle for ss
MutiplexEffects <- includeEffects(MutiplexEffects,transTrip,inPop,name="dis") # add 3-cycle for dis

# Include main effects of the dependent networks on each other's evolution:
MutiplexEffects <- includeEffects(MutiplexEffects,crprod,name="ss",interaction1="dis")
MutiplexEffects <- includeEffects(MutiplexEffects,crprod,name="dis",interaction1="ss")

# include daydic interaction effect within versus between effect
MutiplexEffects <- includeEffects(MutiplexEffects,sameX,name="ss",interaction1="ideology")
MutiplexEffects <- includeEffects(MutiplexEffects,sameX,name="dis",interaction1="ideology")
MutiplexEffects <- includeInteraction(MutiplexEffects,sameX,crprod,name="ss",interaction1=c("ideology","dis"))
MutiplexEffects <- includeEffects(MutiplexEffects,egoX,altX,name="dis",interaction1="activity")

# Create model object:
MutiplexModel <- sienaModelCreate(cond=FALSE,projname="Multiplex-illustration",useStdInits=TRUE)

MutiplexEffects
```

Estimation

```{r}
# Estimate model:
MutiplexResults <- siena07(MutiplexModel,data=MutiplexData,effects=MutiplexEffects,useCluster=T, initC=T,
                           nbrNodes=6,batch=T,verbose=F,returnDeps=TRUE)
# make sure the all convergence ratio < 0.10
MutiplexModel <- sienaModelCreate(cond=FALSE,projname="Multiplex-illustration",useStdInits=F,n3=5000)
MutiplexResults <- siena07(MutiplexModel,data=MutiplexData,effects=MutiplexEffects,prevAns = MutiplexResults,
                           useCluster=T, initC=T,nbrNodes=6,batch=T,verbose=F,returnDeps=TRUE)
MutiplexResults
```

